Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-18 paper/main.tex
starting to fill in methods

\section*{Methods}
\subsection*{Experiment}
\subsubsection*{Participants}
\subsubsection*{Tasks}
\paragraph*{Intake survey.}
\paragraph*{Free recall.}
\paragraph*{Naturalistic recall.}
\paragraph*{Foreign language flashcards.}
\paragraph*{Spatial learning.}

>>>>

    \section*{Methods}

    We ran an online experiment using the Amazon Mechanical Turk
    platform.  We collected data about each participant's fitness and
    exercise habits, a variety of self-reported measures concerning their
    mental health, and about their performance on a battery of memory
    tasks.  We mined the dataset for potential associations between
    memory, mental health, and exercise.

\subsection*{Experiment}
\subsubsection*{Participants}
\begin{itemize}
\item 160 total (recruited ``master'' workers who reported owning and
  using a Fitbit device)
  \item 113 completed all experiments successfully.  We excluded the
    remaining participants who failed to log in to their Fitbit
    accounts, encountered technical issues that prevented them from
    participating in the study, or ended their participation before
    finishing the study.
  \item compensation (check this)
  \item M/F counts
  \item age
    \item demographics (race, education completed, location)
  \end{itemize}
\subsubsection*{Tasks}
\paragraph*{Intake survey.}
\paragraph*{Free recall.}
\paragraph*{Naturalistic recall.}
\paragraph*{Foreign language flashcards.}
\paragraph*{Spatial learning.}
